Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-06 paper/ms.tex
Update published bib record.

\sunanalog\ and \bizarreone\ were identified as a
candidate comoving star pair in our recent search for comoving stars using the
proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr\
(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
We refer the readers to this previous work (\citealt{2016arXiv161202440O}) for a
full explanation of the methodology behind this search and only briefly describe
the method here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
(2) that they have independent 3D velocity vectors, both given only observations
of two components of the velocities (parallaxes and proper motions).
We then select a sample of high-confidence comoving star pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2016arXiv161202440O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.

>>>>

\sunanalog\ and \bizarreone\ were identified as a
candidate comoving star pair in our recent search for comoving stars using the
proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr\
(the astrometric measurements are listed in \tablename~\ref{tab:kk}).
We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
full explanation of the methodology behind this search and only briefly describe
the method here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector, and
(2) that they have independent 3D velocity vectors, both given only observations
of two components of the velocities (parallaxes and proper motions).
We then select a sample of high-confidence comoving star pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2017AJ....153..257O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.
